---
title: "Quorse Notes Overview Presentation"
subtitle: "During the presentation (optional): Get a free github account, install git or GitHub desktop, and open RStudio or VSCode\\newline This workshop is being recorded."
date: 2024-06-07
date-format: "[eCOTS Workshop \\newline ] MMMM DD, YYYY"
---

## Introduction

### Overview

- These are slides... or are they?

::: {.content-visible when-profile="slides"}
If you're reading this, then yes they are!!!
:::

::: {.content-visible when-profile="book"}
If you're reading this, the answer is no! This is a portion that is only visible when compiled as a book!
:::

<!--- \pspace is a special latex command defined in defs_beamer.tex as an empty space to help with slide content, and defined in defs_pdf.tex to do nothing so that the book chapters are not affected. --->

\pspace

This [slideshow]{.content-visible when-profile="slides"} [book chapter created from a slideshow]{.content-visible when-profile="book"} will introduce the basic workflow and some ideas. (Check the source code for this paragraph).

It will be helpful to have a GitHub account, GitHub desktop installed, and RStudio/VSCode running. 

### Workflow Preview

Once everything is set up:

\pspace

- Make slides (or adapt from elsewhere)\lspace
- Add in participation activities\lspace
- Do some live demonstrations in class\lspace
- Push to GitHub after class
    - Everything is now available to the students on a website

### Main Benefits

- Open source and reproducible\lspace
- Easy to use, searchable book for students including all information from class\lspace
- Only one extra step on top of Quarto slides!

## Introduction to Quarto

### `qmd` versus `Rmd`

If you rename `myfile.Rmd` to `myfile.qmd`, it works exactly the same.

`qmd` is the next generation of RMarkdown.

\pspace

- More code options
- More output options
- More language options (python, julia, lua, etc.)
- More editor options

### The General Quarto Idea

One input file, many outputs.

\pspace

- Accepts `qmd`, `Rmd`, and `ipynb` as input files
- Outputs to `pdf`, `html`, `docx`, `pptx`, `md`, `epub`, `odt`, etc.

### Code and Prose

This is text. The following is R code.

```{r}
#| echo: fenced
#| eval: false
print("This is R code, but it won't be executed,")
```

Here's some more text.

```{r}
#| echo: fenced
#| eval: true
print("This is R code, and it will be executed,")
```

### Math, too!

Basic \LaTeX math works in all output formats:

:::: {.columns}
::: {.column width="50%"}
```txt
$$
ma^{th} = f(un)
$$
```

:::
::: {.column width="50%"}
$$
ma^{th} = f(un)
$$
:::
::::

### So Much More!

- Code line numbering, with line highlight.\lspace
- Interactive elements (shiny, runnable code, ).\lspace
- Non-linear slideshows.\lspace
- [So much more!](https://quarto.org/docs/presentations/revealjs/demo/)


## Setup Steps

### The YAML files

**YAML**: Yet Another Markup Language

- Basically, human-readable files that tell a computer what to do. 
- You've seen this syntax if you've used RMarkdown!

\pspace

```yaml
author: "Dr. Devan Becker"
date: "last-modified"
date-format: "iso"

execute:
    warning: false
    cache: true
```


### YAML Separation


:::: {.columns}
::: {.column width="33%"}
`_quarto.yml`

```yml
date-fromat: iso
...

execute:
  warning: false
  ...

profile:
  group:
  - [slides, book]
```
:::
::: {.column width="33%"}
`_quarto-slides.yml`
```yml
project:
  output-dir: Slides

format: 
  beamer:
    ...
    execute:
      echo: false
      ...
```
:::
::: {.column width="33%"}
`_quarto-book.yml`

```yml
project:
  type: book
  output-dir: docs
book:
  title: "Quarto Course Notes"
  ...
  chapters:
    - index.qmd
    ...

format:
  html:
    ...
```
:::
::::

::: {.content-visible when-profile="book"}
- The `_quarto.yml` file includes options that apply to *everything*.
    - The profile group indicates that slides are the default.
- The other two have specific options for slides and book, respectively.
:::

### Special Things in `quarto-book.yml`

- Links to the github repo.\lspace
- Page headers and footers.\lspace
- Navigation options.\lspace
- Chapters (separated into parts) and appendices.\lspace
- Themes/appearance\lspace


### GitHub Pages Workflow

- In `_quarto-slides.yml`, send the outputs whereever
    - I have a folder called "Slides", so I use `project: output-dir: Slides`
- In `quarto-book.yml`, send the outputs to a folder called "`docs`"
    - It must be called `docs` for this to work.
- On GitHub, go to Settings -> Pages
    - Choose "Deploy from a branch"
    - Choose "main" and "docs"

Anytime you push to the repo, the `html` files made by quarto are built into a website!

- Must "build" the `html` files locally.

### Alternative Workflows

- Github pages, but use a different branch
    - Adds some complexity, but allows the source files to be private.\lspace
- Any static site host
    - Set `output-dir` to any folder that gets pushed to the website.
    - Useful if you already have a web host set up.

## Authoring

### Some Conveniences

- Custom beamer definitions for spacing in slides
    - `\lspace` (list space) is a newline in slides, nothing in book.
    - `\pspace` (paragraph space) is a whitespace character in slides, nothing in book\lspace
- Snippets in RStudio
    - `book-only` and `not-book`, but also LaTeX symbols

### Conditional Rendering

- These are slides... or are they?

```
::: {.content-visible when-profile="slides"}
If you're reading this, then yes they are!!!
:::

::: {.content-visible when-profile="book"}
If you're reading this, the answer is no! This is a portion that is only
visible when compiled as a book!
:::
```

RStudio snippets make these really easy!

### Previewing

With the given setup, `Cmd` + `Shift` + `K` will build the *slides* (not book).

\pspace

To see the book you can either: 

1. Run `quarto preview --profile book` in the terminal
    - Quarto will update as you edit!
2. Change the default profile briefly, then change it back.

## Summary

### `qmd` files

- Include code, math, pictures, etc.\lspace
- Render to slides for class.
    - Control what's included.\lspace
- Render to an online book.
    - Include extra content and capabilities.
    - Hosted publicly for free!\lspace
- Add class discussion points, make available where the students expect it.

\pspace

Write once, publish anyywhere!

### Limitations

- Stop making new materials!
    - Search for open source or previous materials, edit for your style!\lspace
- It's always tempting to use the fancy new hotness - be careful!
    - More features = less future proof.\lspace
- If you use my template, you're bound to open source!
    - You can change it substantially and change the license, but the repo is bound to Sharealike.
