# Some advanced things

## webR

Instructions from this [presentation](https://nrennie.rbind.io/teaching-with-webR).

Install the [webR Quarto extension](https://github.com/coatless/quarto-webr):

```sh
quarto add coatless/quarto-webr
```

Add the webR filter to the yaml:

```yaml
format: revealjs
filters:
  - webr
```

Add a webR code block:

````md
```{webr-r}
# set a random seed and generate data
set.seed(123)
x <- rnorm(100)

# calculate mean
mean(x)
```
````

## ShinyLive

[Shiny Live](https://topepo.github.io/shinylive-in-book-test/) allows either R or Python shiny apps to be run from within the book - without storing the book on a shiny server! See [here](https://github.com/RamiKrispin/shinylive-r) for a tutorial.

Every time the user opens your book, the shiny app installs all of the required packages. For best results, keep packages to a minimum.

(This repo does not have an example because the extension adds dependencies. I'll maybe make another repo just to outline the steps I needed to take.)

## Quizzes for your LMS

In my slides, I include something like:

```md
## Q1

Which of the following statements is *False*?

a. True
b. False

<!--- B --->
```

A custom R script extracts the "B" from the comment string, then formats an MC question according to my LMS. 

The question is shown only on the slides, students answer on the LMS.

::: {.content-visible when-profile="book"}
This is specific to the way I do things, but it has saved quite a bit of time and lets me do quizzes tied to their student numbers without an external tool.
:::

## Partially Populated Slides with Full Notes

```{r}
#| echo: true
Sys.getenv("QUARTO_PROFILE")
```

\pspace

Using the profile in R:

```{r}
blank <- function(x) {
    if(Sys.getenv("QUARTO_PROFILE") == "book") {
        return(x)
    } else {
        return("________")
    }
}
```

Forgetful Sally was so forgetful that when she tried to remember something she drew a `r blank("blank")`.


## Solutions (html only)

How can I get an arbitrary block of text to be hidden until the user asks for it?

<details>
<summary>**Solution**</summary>
```md
<details>
<summary>**Solution**</summary>

</details>
```

</details>

## Include from a private repo

You can have a separate repo that is private (e.g., if it has quizzes with solutions), then [include](https://quarto.org/docs/authoring/includes.html) files from that repo. 

- An "include" is a file that is copied verbatim when rendering.
